---
title: "Jstanfield - assignment 3"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(tidyverse)
library(data.table)


fread(file = "./o-ring-erosion-or-blowby.data") -> oringData

str(oringData)

```




### Historical Launch Temperatures and Challenger Launch Day Forecast


```{r}
ggplot(data = oringData, mapping = aes(x = orderflight, y = launchtemp)) +
  geom_point() +
  geom_text(aes(label=launchtemp),hjust=0, vjust=0) +
  geom_hline(yintercept=29, color = 'red') +
  labs(title = "Launch Day Temperatures for Each Shuttle Launch", 
       x = "Temporal order of flight", y = "Launch temperature (degrees F)") +
  theme_linedraw()
```

***   
Here we have the launch day temperatures (F) for all the launches preceding the upcoming Challenger launch.

The red line at the bottom is the predicted temperature for the Challenger launch.





### O-Ring Thermal Distress by Launch Day Temperature

```{r}
ggplot(data = oringData, mapping = aes(x = launchtemp, y = numthermdis)) +
  geom_point() +
  geom_vline(xintercept=29, color = 'red') +
  stat_smooth(method = "loess") +
  scale_x_reverse() +
  labs(title = "Number of O-Rings Experiencing Thermal Distress vs Launch Day Temperature",
       x = "Launch Temperature (Degrees F)", y = "Number of Rings Distressed") +
  theme_linedraw()
  
```


***   
Red Line indicates launch day temperature forecast



